HUME: Human UCCA-Based Evaluation of Machine Translation

### 2016-03-18 paper/main.tex
Cutting down and editing 3.2 and 3.3

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score.
While future extensive empirical evaluation with HUME and its application to MT
system tuning may suggest more complex definition,
as a starting point we take a parsimonious approach,
and compute an accuracy score.

Let $\Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $\Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Let $\Units(s)$ be the total number of units marked with any of the five labels.
Then HUME's composite score is:

@@

We turn to discuss the interface for collecting human judgements on the semantic units
of the source, relating to the translation. UCCA annotations of the source are done offline,
using the UCCA web application.

\figref{fig:interface} presents the user interface of HUME. 
The translation appears at the top, and
the source sentence directly below it. Underneath the source sentence appears
its list of semantic units. For each semantic unit, including the one for the
entire source sentence, there is a textbox, displaying the yield of that unit.
Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the left of the unit's box.

@@

For example, consider the sentence $s=$``We're driving back on Friday'' and the German
translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
``driving back'' will be aligned to ``fahren ... zur\"uck'',
and ``wir'' will be marked as intervening word. Another example
appears in \figref{fig:interface}, where ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing'').

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=1\textwidth]{hume_interface2.jpg}
    \caption{The HUME annotation tool, based on the UCCA tool. The faded orange box at the top
      presents the translation, the large box below it presents the source. The tree of semantic units
      for the source is given underneath, where the aligned text appears in italics, and intervening words
      appear in red with a smaller font (e.g., in the first box).}
    \label{fig:interface}
    \end{center}
\end{figure*}

>>>>

We proceed to detailing how judgements on the semantic units
of the source are aggregated into a composite score. We start by taking a parsiminous approach
%While future extensive empirical evaluation with HUME and its application to MT
%system tuning may suggest more complex definition,
%as a starting point we take a parsimonious approach,
and compute an accuracy score.

Let $\Correct(s,t)$ be the number of atomic units in $s$ marked as Green relative to $t$ plus
the number of structural units in $s$ marked as Adequate relative to $t$.
Let $\Partial(s,t)$ be the number of atomic units in $s$ marked as Orange relative
to $t$. Let $\setsize{\Units(s)}$ be the total number of units marked with any of the five labels.
Then HUME's composite score is:

@@

We now describe the HUME annotation interface, shown in Figure~\figref{fig:interface}. 
%We turn to discuss the interface for collecting human judgements on the semantic units
%of the source, relating to the translation. 
UCCA annotations of the source are done offline,
using the UCCA web application.
%\figref{fig:interface} presents the user interface of HUME. 
The translation appears at the top, and
the source sentence directly below it. Underneath the source sentence appears
its list of semantic units. 
%For each semantic unit, including the one for the
%entire source sentence, there is a textbox, displaying the yield of that unit.
%Information on the category of the unit (e.g., whether it is a Scene, participant etc.).
The user is asked to select a label for each unit,
by clicking the ``A'', ``B'', Green, Orange, or Red buttons to the right of the unit's box.
Note that the UCCA labels are not shown.

@@

For example, 
%consider the sentence $s=$``We're driving back on Friday'' and the German
%translation t=``Am Freitag fahren wir zur\"uck'' (lit. ``on Friday driving we back'').
%``driving back'' will be aligned to ``fahren ... zur\"uck'',
%and ``wir'' will be marked as intervening word. Another example
in \figref{fig:interface}, ``ongoing pregnancy'' is translated to
``Schwangerschaft ... laufenden'' (lit. ``pregnancy ... ongoing''). The interleaving 
German words shown in red should not occur there, and the annotator should take this
into account and mark this structural node as ``B'', bad.

@@

\begin{figure*}[t]
    \begin{center}
    \includegraphics[width=1\textwidth]{hume_interface2.jpg}
    \caption{The HUME annotation tool, based on the UCCA tool. The faded orange box at the top
      contains the translation, and directly below it is the source sentence. The tree of semantic units
      is shown below the source. Alignments between the source and translation appear in italics and unaligned intervening words appear in red.}
    \label{fig:interface}
    \end{center}
\end{figure*}
